---
title: '#TidyTuesday 40 1.10.2019: All the Pizza'
author: "teofil"
date: "3/10/2019"
output:
  html_document:
  df_print: paged
toc: true
---
  
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(ggrepel)
library(ggpubr)
```

```{r}
pizza_barstool <-
  readr::read_csv(
    "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-01/pizza_barstool.csv"
  )

```

```{r}
vv <- viridis::viridis(n = 9, alpha = .8, begin = .2 ,option = "C")[c(1,5,9)]
```

# Compare how pizzerias are rated by community vs. Dave

First grab just columns we need

```{r}
pzbs <-
  pizza_barstool %>%
  dplyr::select(name,
                address = address1,
                city,
                tidyselect::contains("average_score")) %>%
  filter(review_stats_community_average_score > 0)%>%
  filter(review_stats_dave_average_score > 0.2)
```


## Some more wrangling

Calculate the other two dataset that we created in the exploratory session .Color the pizzerias based on the degree of rating disagreement. First lets calculate the difference in rating.
```{r}
rate_diff <-
  pzbs %>%
  mutate(difference =
           review_stats_community_average_score - review_stats_dave_average_score)  %>% 
  mutate(agreement=1/difference)

```

Highlight points (outliers, influential values,..). We need another dataset, this time for the five pizzerias with largest negative and positive difference.

```{r}
rate_diff_top5 <- rate_diff %>%
  mutate(pos_neg = ifelse(difference > 0, "preferred by community", "preferred by dave")) %>%
  group_by(pos_neg) %>%
  top_n(n = 5, wt = abs(difference)) %>% 
  ungroup
```

More modifications to this data frame  to make coordinates for segments  for manual labels.

```{r}
rdt5 <- 
  rate_diff_top5 %>% 
  mutate(name_city= paste(name, "\n(", city, ")", sep="")) %>% 
  select(name, name_city, contains("dave"), contains("community"), pos_neg, difference) %>% 
  arrange(pos_neg, desc(difference)) %>% 
  mutate(xend=c(rep(10.1,5), rep(2.4, 5))) %>% 
  mutate(yend=c(5,2,3,4,6, 7,6,10,9,8)) %>% 
  rename(x=review_stats_community_average_score,
         y=review_stats_dave_average_score)
```

## Now we should have everything to build the plot

### geoms
```{r}
PP <-
  ggplot(data = pzbs) +
  geom_abline(slope = 1,
              intercept = 0,
              linetype = 2) +
  aes(x = review_stats_community_average_score) +
  aes(y = review_stats_dave_average_score) +
  geom_point(
    data = rate_diff,
    inherit.aes = TRUE,
    color = "white",
    aes(size = abs(difference), fill = difference),
    pch = 21
  ) +
  geom_segment(
    data = rdt5,
    size = .5,
    linetype = 3,
    aes(
      x = x,
      y = y,
      xend = xend,
      yend = yend
    )
  ) +
  geom_label(
    data = rdt5,
    aes(
      x = xend,
      y = yend,
      fill = difference,
      label = str_wrap(name, 22)
    ),
    size = 3.5,
    hjust = c(rep(0, 5), rep(1, 5))
  )
```

### scales

```{r}
PP <- PP +
  scale_fill_gradient2(
    name = "",
    low = vv[1],
    mid = vv[2],
    high = vv[3],
    limits = c(-5, 7.5),
    breaks = c(-5,-2.5, 0, 2.5, 5, 7.5),
    labels = c(
      "Dave's favorites\nrated low by the community",
      "",
      "",
      "",
      "",
      "Community favorites\nrated low by Dave"
    ),
    guide = guide_colourbar(
      title.vjust = 1,
      frame.colour = 'white',
      label.position = "top",
      frame.linewidth = 1,
      ticks.colour = 'white',
      ticks.linewidth = 2,
      barheight = unit(.30, "cm"),
      barwidth = unit(8, "cm"),
      draw.ulim = TRUE,
      draw.llim = TRUE
    )
  ) +
  scale_y_continuous(breaks = seq(0, 10, 2), limits = c(0, 12)) +
  scale_x_continuous(breaks = seq(0, 10, 2), limits = c(0, 12)) +
  scale_size_continuous(range = c(0.5, 8), guide = "none")
```

## Labs

```{r}
PP <- PP +
  labs(x = "Community rating (average)") +
  labs(y = "Dave's rating") +
  labs(title = "Trust Dave?") +
  labs(subtitle = "Or follow the crowd?") +
  labs(caption = "TidyTuesdayAtKIKA using pizza_barstool data")
```

## Theme

```{r}
PP <- PP +
  theme_minimal() +
  theme(legend.position = 'bottom') +
  theme(panel.background = element_rect(fill = "grey80", color = "white")) +
  theme(plot.background = element_rect(fill = "grey80", color = "grey60")) +
  theme(axis.title = element_text(hjust = 1, size = 12)) +
  theme(axis.text = element_text(hjust = 1, size = 10))
  
PP

```

# Other ways to label stuff
```{r, eval = FALSE}
 +
   geom_label_repel(
     data = rate_diff_top5, force=10,
     aes(x = review_stats_community_average_score,
         y = review_stats_dave_average_score,
         label = name,
         fill=difference),
     alpha=.8,
     inherit.aes = FALSE
   )
```

# Function to make fancy labels

```{r, eval = FALSE}
 library(ggforce)
 gmark <- function(row) {
   geom_mark_circle(
   data = row,
   label.fontsize = 8,
   label.fill = NA,
   aes(x = review_stats_community_average_score,
       y = review_stats_dave_average_score,
       label = name),
   inherit.aes = FALSE
 )
 }
PP + map(1:10, function(x) slice(rate_diff_top5, x) %>% gmark)
```